\HeaderA{codling}{Dose-mortality data, for fumigation of codling moth with methyl bromide}{codling}
\keyword{datasets}{codling}
\begin{Description}\relax
Data are from trials that studied the mortality response of codling moth
to fumigation with methyl bromide.
\end{Description}
\begin{Usage}
\begin{verbatim}data(codling)\end{verbatim}
\end{Usage}
\begin{Format}\relax
A data frame with 99 observations on the following 10 variables.
\describe{
\item[dose] Injected dose of methyl bromide, in gm per cubic meter
\item[tot] Number of insects in chamber
\item[dead] Number of insects dying
\item[pobs] Proportion dying
\item[cm] Control mortality, i.e., at dose 0
\item[ct] Concentration-time sum
\item[Cultivar] a factor with levels \code{BRAEBURN} \code{FUJI} \code{GRANNY} \code{Gala} \code{ROYAL} \code{Red Delicious} \code{Splendour}
\item[gp] a factor which has a different level for each different
combination of \code{Cultivar}, \code{year} and \code{rep} (replicate).
\item[year] a factor with levels \code{1988} \code{1989}
\item[numcm] a numeric vector: total number of control insects
}
\end{Format}
\begin{Details}\relax
The research that generated these data was in part funded by New Zealand
pipfruit growers.  The published analysis was funded by New Zealand
pipfruit growers. See also \code{sorption}.
\end{Details}
\begin{Source}\relax
Maindonald, J.H.; Waddell, B.C.; Petry, R.J. 2001.
Apple cultivar effects on codling moth (Lepidoptera: Tortricidae)
egg mortality following fumigation with methyl bromide.
Postharvest Biology and Technology 22: 99-110.
\end{Source}

