\HeaderA{humanpower}{Oxygen uptake versus mechanical power, for humans}{humanpower}
\aliasA{humanpower1}{humanpower}{humanpower1}
\aliasA{humanpower2}{humanpower}{humanpower2}
\keyword{datasets}{humanpower}
\begin{Description}\relax
The data set from Daedalus project.
\end{Description}
\begin{Usage}
\begin{verbatim}data(humanpower1)\end{verbatim}
\end{Usage}
\begin{Format}\relax
A data frame with 28 observations on the following 3 variables.
\describe{
\item[wattsPerKg] a numeric vector: watts per kilogram of body weight
\item[o2] a numeric vector: ml/min/kg
\item[id] a factor with levels 1 - 5 (\code{humanpower1})
or 1 - 4 (\code{humanpower2}), identifying the different athletes
}
\end{Format}
\begin{Details}\relax
Data in \code{humanpower1} are from investigations (Bussolari 1987)
designed to assess the feasibility of a proposed 119 kilometer human
powered flight from the island of Crete -- in the initial phase of the
Daedalus project.  Data are for five athletes
-- a female hockey player, a male amateur tri-athlete, a female
amateur triathlete, a male wrestler and a male cyclist -- who were
selected from volunteers who were recruited through the news media,
Data in \code{humanpower2) are for four out of the 25 applicants who
    were selected for further testing, in the lead-up to the eventual
    selection of a pilot for the Daedalus project (Nadel and Bussolari 1988).
}
\end{Details}
\begin{Source}\relax
Bussolari, S.R.(1987). Human factors of long-distance human-powered
aircraft flights.  Human Power 5: 8-12.

Nadel and Bussolari, S.R.(1988). The Daedalus project: physiological
problems and solutions.  American Scientist 76: 351-360.
\end{Source}
\begin{References}\relax
Nadel and Bussolari, S.R.(1989). The physiological limits of
long-duration human-power production -- lessons learned from
the Daedalus project.  Human Power 7: 7-10.
\end{References}
\begin{Examples}
\begin{ExampleCode}
str(humanpower1)
plot(humanpower1)
lm(o2 ~ id + wattsPerKg:id, data=humanpower1)
lm(o2 ~ id + wattsPerKg:id, data=humanpower2)
\end{ExampleCode}
\end{Examples}

