\HeaderA{nsw74psid1}{Labour Training Evaluation Data}{nsw74psid1}
\keyword{datasets}{nsw74psid1}
\begin{Description}\relax
This data frame contains 2675 rows and 10 columns.
These data are pertinent to an investigation of the way that   
earnings changed, between 1974-1975 and 1978, in the absence
of training.  Data for the experimental treatment 
group (NSW) were combined with control data results from the 
Panel Study of Income Dynamics (PSID) study.
\end{Description}
\begin{Usage}
\begin{verbatim}nsw74psid1\end{verbatim}
\end{Usage}
\begin{Format}\relax
This data frame contains the following columns:
\describe{
\item[trt] a numeric vector 
identifying the study in which the subjects were enrolled
(0 = PSID, 1 = NSW).
\item[age] age (in years).
\item[educ] years of education.
\item[black] (0 = not black, 1 = black).
\item[hisp] (0 = not hispanic, 1 = hispanic).
\item[marr] (0 = not married, 1 = married).
\item[nodeg] (0 = completed high school, 1 = dropout).
\item[re74] real earnings in 1974.
\item[re75] real earnings in 1975.
\item[re78] real earnings in 1978. 
}
\end{Format}
\begin{Source}\relax
http://www.columbia.edu/~rd247/nswdata.html
\end{Source}
\begin{References}\relax
Dehejia, R.H. and Wahba, S. 1999. Causal effects in
non-experimental studies: re-evaluating the evaluation of training
programs. Journal of the American Statistical Association 94:
1053-1062.

Lalonde, R. 1986. Evaluating the economic evaluations of
training programs. American Economic Review 76: 604-620.
\end{References}
\begin{Examples}
\begin{ExampleCode}
print("Interpretation of Regression Coefficients - Example 6.6")

 nsw74psid1.lm <- lm(re78~ trt+ (age + educ + re74 + re75) +
   (black + hisp + marr + nodeg), data = nsw74psid1)
 summary(nsw74psid1.lm)$coef
options(digits=4)
sapply(nsw74psid1[, c(2,3,8,9,10)], quantile, prob=c(.25,.5,.75,.95,1))
attach(nsw74psid1)
sapply(nsw74psid1[trt==1, c(2,3,8,9,10)], quantile, 
prob=c(.25,.5,.75,.95,1))
pause()

here <- age <= 40 & re74<=5000 & re75 <= 5000 & re78 < 30000 
nsw74psidA <- nsw74psid1[here, ]
detach(nsw74psid1)
table(nsw74psidA$trt)
pause()

A1.lm <- lm(re78 ~ trt + (age + educ + re74 + re75) + (black +
      hisp + marr + nodeg), data = nsw74psidA)
summary(A1.lm)$coef
pause()

A2.lm <- lm(re78 ~ trt + (age + educ + re74 + re75) * (black +   
      hisp + marr + nodeg), data = nsw74psidA)
anova(A1.lm, A2.lm)

\end{ExampleCode}
\end{Examples}

